Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2017-01-17 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Make some updates on paper draft

#devtools::install_github("leighseverson/countyweather")
options("noaakey" = Sys.getenv("noaakey"))
library(countyweather)

@@

```{r all_storms, echo = FALSE, fig.align = 'center', fig.cap = "Tracks of tropical cyclones included in this study. Darker tracks indicate storms whose names were retired.", message = FALSE}
# Map of tracks of all storms in study.
a <- map_tracks(storms, plot_points = FALSE, alpha = 0.3, color = "darkcyan")
# Add storms whose names were retired
# Source: http://www.nhc.noaa.gov/aboutnames_history.shtml
map_tracks(c("Hugo-1989", "Bob-1991", "Andrew-1992", 
             "Opal-1995", "Fran-1996", "Georges-1998", "Mitch-1998",
             "Floyd-1999", "Allison-2001", "Michelle-2001",
             "Isidore-2002", "Lili-2002", "Isabel-2003",
             "Charley-2004", "Frances-2004",
             "Ivan-2004", "Jeanne-2004", 
             "Dennis-2005", "Katrina-2005", "Rita-2005",
             "Wilma-2005", "Noel-2007",
             "Gustav-2008", "Ike-2008", "Paloma-2008",
             "Irene-2011"),
           plot_object = a, plot_points = FALSE, color = "darkcyan") + 
        theme(panel.grid.major = element_blank(),
           panel.grid.minor = element_blank(),
           panel.background = element_rect(colour = "black", size = 1))
```

@@

```{r frances_rain_flood_exp, echo = FALSE, fig.width = 6, fig.height = 8, fig.align = "center", fig.cap = "Counties that were classified as 'exposed' to Hurricane Frances (2004) based on rain (top) and flood event (bottom) exposure criteria. Rain-based exposure was assessed based on storm-associated rainfall of 75 millimeters or more in the county and a distance of 500 kilometers or less between the county's population mean center and the storm's closest approach. Flood event-based exposure was based on the county have a flood event listing in the NOAA Storm Events database and being within [x] kilometers of the storm's track."}
storm <- "Frances-2004"
a <- map_tracks(storms = storm, plot_points = FALSE, 
                plot_object = map_rain_exposure(storm = storm, 
                                           dist_limit = 500,
                                           rain_limit = 75)) + 
        ggtitle("Rain-based exposure during Frances, 2004")
b <- map_tracks(storms = storm, plot_points = FALSE, 
                plot_object = map_event_exposure(storm = storm, 
                                           event_type = "flood")) + 
        ggtitle("Flood events during Frances, 2004")
grid.arrange(a, b, ncol = 1)
```

```{r floyd_rain_flood_exp, echo = FALSE, fig.width = 6, fig.height = 8, fig.align = "center", fig.cap = "Counties that were classified as 'exposed' to Hurricane Floyd (1999) based on rain (top) and flood event (bottom) exposure criteria. Rain-based exposure was assessed based on storm-associated rainfall of 75 millimeters or more in the county and a distance of 500 kilometers or less between the county's population mean center and the storm's closest approach. Flood event-based exposure was based on the county have a flood event listing in the NOAA Storm Events database and being within [x] kilometers of the storm's track."}
storm <- "Floyd-1999"
a <- map_tracks(storms = storm, plot_points = FALSE, 
                plot_object = map_rain_exposure(storm = storm, 
                                           dist_limit = 500,
                                           rain_limit = 75)) + 
        ggtitle("Rain-based exposure during Floyd, 1999")
b <- map_tracks(storms = storm, plot_points = FALSE, 
                plot_object = map_event_exposure(storm = storm, 
                                           event_type = "flood")) + 
        ggtitle("Flood events during Floyd, 1999")
grid.arrange(a, b, ncol = 1)
```

>>>>

options("noaakey" = Sys.getenv("noaakey"))
library(countyweather)

@@

```{r all_storms, echo = FALSE, fig.align = 'center', fig.cap = "Tracks of tropical cyclones included in this study. Darker tracks indicate storms whose names were retired.", message = FALSE}
# Map of tracks of all storms in study.
a <- map_tracks(storms, plot_points = FALSE, alpha = 0.3, color = "darkcyan")
# Add storms whose names were retired
# Source: http://www.nhc.noaa.gov/aboutnames_history.shtml
map_tracks(c("Hugo-1989", "Bob-1991", "Andrew-1992", 
             "Opal-1995", "Fran-1996", "Georges-1998", "Mitch-1998",
             "Floyd-1999", "Allison-2001", "Michelle-2001",
             "Isidore-2002", "Lili-2002", "Isabel-2003",
             "Charley-2004", "Frances-2004",
             "Ivan-2004", "Jeanne-2004", 
             "Dennis-2005", "Katrina-2005", "Rita-2005",
             "Wilma-2005", "Noel-2007",
             "Gustav-2008", "Ike-2008", "Paloma-2008",
             "Irene-2011"),
           plot_object = a, plot_points = FALSE, color = "darkcyan") + 
        theme(panel.grid.major = element_blank(),
           panel.grid.minor = element_blank(),
           panel.background = element_rect(colour = "black", size = 1)) + 
        coord_map()
```

@@

```{r frances_rain_flood_exp, echo = FALSE, fig.width = 6, fig.height = 8, fig.align = "center", fig.cap = "Counties that were classified as 'exposed' to Hurricane Frances (2004) based on rain (top) and flood event (bottom) exposure criteria. Rain-based exposure was assessed based on storm-associated rainfall of 75 millimeters or more in the county and a distance of 500 kilometers or less between the county's population mean center and the storm's closest approach. Flood event-based exposure was based on the county have a flood event listing in the NOAA Storm Events database and being within 500 kilometers of the storm's track."}
storm <- "Frances-2004"
a <- map_tracks(storms = storm, plot_points = FALSE, 
                plot_object = map_rain_exposure(storm = storm, 
                                           dist_limit = 500,
                                           rain_limit = 75)) + 
        ggtitle("Rain-based exposure during Frances, 2004")
b <- map_tracks(storms = storm, plot_points = FALSE, 
                plot_object = map_event_exposure(storm = storm, 
                                           event_type = "flood")) + 
        ggtitle("Flood events during Frances, 2004")
grid.arrange(a, b, ncol = 1)
```

```{r floyd_rain_flood_exp, echo = FALSE, fig.width = 6, fig.height = 8, fig.align = "center", fig.cap = "Counties that were classified as 'exposed' to Hurricane Floyd (1999) based on rain (top) and flood event (bottom) exposure criteria. Rain-based exposure was assessed based on storm-associated rainfall of 75 millimeters or more in the county and a distance of 500 kilometers or less between the county's population mean center and the storm's closest approach. Flood event-based exposure was based on the county have a flood event listing in the NOAA Storm Events database and being within 500 kilometers of the storm's track."}
storm <- "Floyd-1999"
a <- map_tracks(storms = storm, plot_points = FALSE, 
                plot_object = map_rain_exposure(storm = storm, 
                                           dist_limit = 500,
                                           rain_limit = 75)) + 
        ggtitle("Rain-based exposure during Floyd, 1999")
b <- map_tracks(storms = storm, plot_points = FALSE, 
                plot_object = map_event_exposure(storm = storm, 
                                           event_type = "flood")) + 
        ggtitle("Flood events during Floyd, 1999")
grid.arrange(a, b, ncol = 1)
```
